Estimating duration in the presence of misclassification

### 2024-08-02 incidence-prevalence.tex
Rob p.65 comment

Considering multiple values of $t$ makes \cref{inc-prev:eq:EPt} into a system of simultaneous equations.
Therefore, the system can be written in matrix form:
\begin{align}
  \E(\vec{P} \mid \vec{Z}) = \matr{S} \vec{Z}. \label{inc-prev:eq:EPt-matrix} \\
\intertext{$\matr{S}$ is a lower-triangular matrix formed from $S$:}
    (\matr{S})_{i,j} &= \begin{cases}
        S(i - j + 1) & i - \dmax - 1 \leq j \leq i \\
        0 & \text{otherwise.}
    \end{cases} \label{inc-prev:eq:Smatrix}
\end{align}
where $\vec{P} = [P_1, P_2, \dots]$.
In \cref{E-backcalc}, I will need to solve for this system for $\vec{Z}$ given a known $\hat{P} = \E(\vec{P} \mid {Z})$.
Assuming $\vec{P}$ and $\vec{Z}$ have the same dimension then $\matr{S}$ is lower-triangular with strictly positive diagonal elements; therefore, $\matr{S}$ is invertible, and the system has a unique solution~\autocite[424]{bernsteinFacts}.
The lower-triangular structure of $\matr{S}$ allows solving the system through forward-substitution, an efficient method that avoids explicit matrix inversion~\autocite{cormenMatrix}.
Forward-substitution sequentially solves the $t$th element of $\vec{Z}$ ($t = 1, \dots, T$) by calculating:
\begin{align}
Z_t
&= \frac{\hat{P}_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
&= \hat{P}_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
\label{inc-prev:eq:forward-substitute}
\end{align}
where $S(t)$ for $t > \dmax$ is defined to be 0.

>>>>

Considering multiple values of $t$ makes \cref{inc-prev:eq:EPt} into a system of simultaneous equations.
Therefore, the system can be written in matrix form:
\begin{align}
  \E(\vec{P} \mid \vec{Z}) = \matr{S} \vec{Z}. \label{inc-prev:eq:EPt-matrix} \\
\intertext{$\matr{S}$ is a lower-triangular matrix formed from $S$:}
    (\matr{S})_{i,j} &= \begin{cases}
        S(i - j + 1) & \text{if } i - \dmax + 1 \leq j \leq i \\
        0 & \text{otherwise.}
    \end{cases} \label{inc-prev:eq:Smatrix}
\end{align}
where $\vec{P} = [P_1, P_2, \dots]$.
In \cref{E-backcalc}, I will need to solve for this system for $\vec{Z}$ given a known $\hat{P} = \E(\vec{P} \mid {Z})$.
Assuming $\vec{P}$ and $\vec{Z}$ have the same dimension then $\matr{S}$ is lower-triangular with strictly positive diagonal elements; therefore, $\matr{S}$ is invertible, and the system has a unique solution~\autocite[424]{bernsteinFacts}.
The lower-triangular structure of $\matr{S}$ allows solving the system through forward-substitution, an efficient method that avoids explicit matrix inversion~\autocite{cormenMatrix}.
Forward-substitution sequentially solves the $t$th element of $\vec{Z}$ ($t = 1, \dots, T$) by calculating:
\begin{align}
Z_t
&= \frac{\hat{P}_t - \sum_{i=1}^{t-1} S_{ti} Z_i}{S_{tt}} \\
&= \hat{P}_t - \sum_{i=1}^{t-1} S(t - i + 1) Z_i.
\label{inc-prev:eq:forward-substitute}
\end{align}
where $S(t)$ for $t > \dmax$ is defined to be 0.
